Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2015-02-16 doc/GMP2015/revision_1/s03_drp.tex
Compiles with Elsevier format. Got rid of minor spacing errors. Converted tikz figures to eps. Aligned subfigures. Etc. It's looking good! Now to consider major changes.

This theorem (proven in the Appendix) relies on the following crucial observation and lemma
that are also used for other types of qusecs in the Application sections (\ref{sec:bodypin}, \ref{sec:pinnedline}) of
the paper.

@@

    \item\label{lemma:wc_intersection_makes_all_wc}
    If $C_i\cup C_j$ is isostatic, then $\forall k: C_i\cup C_k$ is isostatic Alternatively, if $C_i\cup C_j=C$, then $\forall k: C_i\cup C_k=C$.

@@

\begin{figure*}\centering
\begin{subfigure}{.3\linewidth}\centering
    \input{img/tikz/c2c3_of_k33s-0.tikz}
    \caption{}\label{fig:c2c3ofk33s:a}
\end{subfigure}%
\begin{subfigure}{.7\linewidth}\centering
    \input{img/tikz/c2c3_of_k33s-1.tikz}
    \caption{}\label{fig:c2c3ofk33s:b}
\end{subfigure}

\caption{(\ref{fig:c2c3ofk33s:a}) A doublet ($C_2 \times C_3$) with each edge of the triangles replaced by a $K_{3,3}$. This pattern continues inwards for a total of $N$ triangles, indicated by the dashed lines. (\ref{fig:c2c3ofk33s:b}) Most of the DR-plan of this graph, omitting further decomposition of $K_{3,3}$ subgraphs into the separate 9 edges and of edges into the component nodes. $G\setminus\{a_i,b_i,c_i\}$ is shorthand for $G$ difference those nodes and all of the nodes in the corresponding $K_{3,3}$ subgraphs. The dashed lines indicated that this exact structure is repeated.}
\label{fig:c2c3ofk33s}
\end{figure*}

>>>>

This theorem (proven in the \ref{theorem:main:proof}) relies on the following crucial observation and lemma that are also used for other types of qusecs in the Application sections (\ref{sec:bodypin}, \ref{sec:pinnedline}) of the paper.

@@

    \item\label{lemma:wc_intersection_makes_all_wc}
    If $C_i\cup C_j$ is isostatic, then $\forall k: C_i\cup C_k$ is isostatic. Alternatively, if $C_i\cup C_j=C$, then $\forall k: C_i\cup C_k=C$.

@@

% \begin{figure*}\centering
% \begin{subfigure}{.3\linewidth}\centering
%     \input{img/tikz/c2c3_of_k33s-0.tikz}
%     \caption{}\label{fig:c2c3ofk33s:a}
% \end{subfigure}%
% \begin{subfigure}{.7\linewidth}\centering
%     \input{img/tikz/c2c3_of_k33s-1.tikz}
%     \caption{}\label{fig:c2c3ofk33s:b}
% \end{subfigure}

% \caption{(\ref{fig:c2c3ofk33s:a}) A doublet ($C_2 \times C_3$) with each edge of the triangles replaced by a $K_{3,3}$. This pattern continues inwards for a total of $N$ triangles, indicated by the dashed lines. (\ref{fig:c2c3ofk33s:b}) Most of the DR-plan of this graph, omitting further decomposition of $K_{3,3}$ subgraphs into the separate 9 edges and of edges into the component nodes. $G\setminus\{a_i,b_i,c_i\}$ is shorthand for $G$ difference those nodes and all of the nodes in the corresponding $K_{3,3}$ subgraphs. The dashed lines indicated that this exact structure is repeated.}
% \label{fig:c2c3ofk33s}
% \end{figure*}

% \FigInit
%     {(\ref{fig:c2c3ofk33s:a}) A doublet ($C_2 \times C_3$) with each edge of the triangles replaced by a $K_{3,3}$. This pattern continues inwards for a total of $N$ triangles, indicated by the dashed lines. (\ref{fig:c2c3ofk33s:b}) Most of the DR-plan of this graph, omitting further decomposition of $K_{3,3}$ subgraphs into the separate 9 edges and of edges into the component nodes. $G\setminus\{a_i,b_i,c_i\}$ is shorthand for $G$ difference those nodes and all of the nodes in the corresponding $K_{3,3}$ subgraphs. The dashed lines indicated that this exact structure is repeated.}
%     {fig:c2c3ofk33s}
% \FigTwoSubfigWithWidth
%     {.3}
%     {img/epsfromtikz/c2c3_of_k33s-0}
%     {}
%     {fig:c2c3ofk33s:a}
%     %
%     {.7}
%     {img/epsfromtikz/c2c3_of_k33s-1}
%     {}
%     {fig:c2c3ofk33s:b}

\ClearMyMinHeight
\SetMyMinHeight{.3}{img/epsfromtikz/c2c3_of_k33s-0}
\SetMyMinHeight{.7}{img/epsfromtikz/c2c3_of_k33s-1}

\begin{figure*}\centering%
    %
    \begin{subfigure}{0.3\linewidth}\centering
        \includegraphics[height=\myMinHeight]{img/epsfromtikz/c2c3_of_k33s-0}
        \caption{}\label{fig:c2c3ofk33s:a}
    \end{subfigure}%
    %
    \hfill
    \begin{subfigure}{0.7\linewidth}\centering
        \includegraphics[height=\myMinHeight]{img/epsfromtikz/c2c3_of_k33s-1}
        \caption{}\label{fig:c2c3ofk33s:b}
    \end{subfigure}%
    %
    \caption{(\ref{fig:c2c3ofk33s:a}) A doublet ($C_2 \times C_3$) with each edge of the triangles replaced by a $K_{3,3}$. This pattern continues inwards for a total of $N$ triangles, indicated by the dashed lines. (\ref{fig:c2c3ofk33s:b}) Most of the DR-plan of this graph, omitting further decomposition of $K_{3,3}$ subgraphs into the separate 9 edges and of edges into the component nodes. $G\setminus\{a_i,b_i,c_i\}$ is shorthand for $G$ difference those nodes and all of the nodes in the corresponding $K_{3,3}$ subgraphs. The dashed lines indicated that this exact structure is repeated.}
    \label{fig:c2c3ofk33s}
\end{figure*}%

### 2015-02-16 doc/GMP2015/revision_1/s04_recombination.tex
Compiles with Elsevier format. Got rid of minor spacing errors. Converted tikz figures to eps. Aligned subfigures. Etc. It's looking good! Now to consider major changes.

The main barrier in recombination when given an optimal DR-plan (of
smallest possible size or max fan-in),  is that the number of children
(resp. number of roots) --- and correspondingly the  size and complexity
of the (indecomposable) algebraic system $I$ to be solved --- could be
arbitrarily large as a function of the size of the input system. This
difficulty can persist even after optimal parametrization of the
indecomposable system $I$ as in \cite{sitharam2010optimized} to minimize its algebraic
complexity.

@@

\medskip\noindent
\header{(a) Small DR-plan.} We obtain a  parameterized family of systems
$I_{\lambda_F}$ --- one for each value $\lambda_F$ for the parameters
$F$,  all of which have small DR-plans. Thus, given a value $v$ for
$\lambda_F$, the system $I_v$ can potentially be solved or realized
easily once the orientation type of the solution is known  (when the
DR-plan size is small enough).

@@

% \begin{proof}
%     The Cartesian realization space of $(H,\left<\delta_{E'},
%     \lambda_F\right>)$ is computed easily with a DR-plan of size 2,
%     and is the union of $2^t$ solutions (modulo orientation preserving
%     isometries) each with a distinct orientation type, where $t$ is
%     the number of triangles in the 2-tree $H$; here $\delta_{S}$ is
%     the restriction of the length vector $\delta$ to the edges in $S$.
%     A desired solution $p$ (or connected component of a solution
%     space) of $(G,\delta)$ of an orientation type $\sigma_p$ can be
%     found by a subdivided binary search   of the cartesian realization
%     space of $(H, \left<\delta_{E'}, \lambda_F\right>)$ of orientation
%     type $\sigma_p$ - as $\lambda_F$ ranges over the discretized
%     convex polytope $\Phi_F(G',\delta_E')$ with bounding hyperplanes
%     described in Theorem \ref{theorem:convexcayley}. A solution $p$
%     is found  when the lengths for nonedges in $D$ match $\delta_D$.
% \end{proof}
%
\begin{figure*}\centering
\begin{subfigure}{.2\linewidth}\centering
    \input{img/tikz/omd_k33_example_new-0.tikz}
    \caption{}\label{fig:omd_k33_example:a}
\end{subfigure}\hfill
\begin{subfigure}{.15\linewidth}\centering
    \input{img/tikz/omd_k33_example_new-1.tikz}
    \caption{}\label{fig:omd_k33_example:b}
\end{subfigure}
\begin{subfigure}{.15\linewidth}\centering
    \input{img/tikz/omd_k33_example_new-2.tikz}
    \caption{}\label{fig:omd_k33_example:c}
\end{subfigure}\hfill
\begin{subfigure}{.15\linewidth}\centering
    \input{img/tikz/omd_k33_example-1.tikz}
    \caption{}\label{fig:omd_k33_example:d}
\end{subfigure}
\begin{subfigure}{.15\linewidth}\centering
    \input{img/tikz/omd_k33_example-2.tikz}
    \caption{}\label{fig:omd_k33_example:e}
\end{subfigure}

@@

\noindent
\note A major advantage of the convex Cayley method is that it is
completely unaffected when $\delta$ are intervals rather than exact
values~~\cite{sitharam2010convex}.
%cite my paper with Heping!!!

\myexample
[Using Cayley configuration space].
A graph $G=K_{3,3}$  cannot be decomposed into any nontrivial
isostatic graphs, i.e, its DR-plan has a root and 9 children
corresponding to the 9 edges. Solving or recombining the system
$(G,\delta)$ corresponding to the root of this DR-plan involves
solving a quadratic system with 8 equations and variables. Instead of
simultaneously solving this system, we could instead use the fact that
$G=K_{3,3}$ is in OMD$_2$: remove the edges $e_1,e_2$ in Figure
\ref{fig:omd_k33_example} to give a partial 2-tree $G'$. Now add the
nonedges $f_1,f_2$ to give a 2-tree $H$ with a DR-plan of size 2. The Cayley
configuration space $\Phi_f(G', \delta_{E\setminus e})$ is a single
interval of attainable length values $\lambda_F$ for the edge $f$.
When $\delta$ is generic, i.e, does not admit collinearities or
coincidences in the realizations of $(G,\delta)$, the realization
space of $(H, \left<\delta_{E\setminus e}, \lambda_f\right>)$ has 16
solutions $q^p_{\lambda_f}$ (modulo orientation preserving
isometries), with distinct orientation types $\sigma_p$ (two
orientation choices for each of the 4 triangles) that can be obtained
by solving a sequence of 4 single quadratics in 1 variable (DR-plan of
size 2). By subdivided binary search in the interval $\lambda_f \in
\Phi_f(G', \delta_{E\setminus e})$, the desired solution $p$  of
$(G,\delta)$ is found when the length of the nonedge $e$ in  the
realization $q^p_{\lambda_f}$ is $\delta_e$.

In fact, we can show that $G=K_{3,3}$ is in OMD$_1$ by removing a single
edge to reduce (as shown in Figure \ref{fig:omd_k33_example}) to a
tree-decomposable graph of low Cayley complexity (which includes the class
of partial 2-trees).
In the next Section \ref{sec:tdecomp}, we discuss this issue
of why the largest class of reduced graphs is desirable.
%
\subsection{Optimized Modification by Enlarging the class of Reduced
Graphs}
\label{sec:tdecomp}
%
It is possible in principle to decrease $k$ for a OMD$_k$ graph (i.e,
the number of edges to be removed to ensure an isostatic completion
that is decomposable with a small DR-plan) by considering reduced
graphs $G'$ (and modified graphs $H$) that come from a larger class
than partial 2-trees but nevertheless have convex Cayley configuration
spaces at least when the realization space is restricted to a
sufficiently comprehensive orientation type. In particular, the so-
called \dfn{tree-decomposable graphs of low Cayley complexity}
\cite{sitharam2011cayleyI,sitharam2011cayleyII} include the partial 2-trees and many others that are not
partial 2-trees. See an illustration in Figure \ref{fig:omd_k33_example}.
These too result in DR-plans of size 2 or 3, putting
$G$ in the class OMD$_k$ and thus meeting Criteria (a) and (b). The
Criterion (c) is met --- for example when $k=1$ --- because 1-dof Cayley
configuration spaces of linkages based on such graphs $G'$ are known
to be single intervals when a comprehensive orientation type
$\sigma_p$ of the sought solution $p$ is given. In addition, the
bounds of these intervals are of low algebraic complexity. More
precisely, the bounds  can themselves be computed using a DR-plan of
size 2 or 3, i.e, the computation of these bounds is tree-
decomposable. Alternatively, the bounds are in a simple quadratic or
radically solvable extension field over the rationals, or can be
computed by solving a triangularized system of quadratics.

>>>>

The main barrier in recombination when given an optimal DR-plan (of smallest possible size or max fan-in),  is that the number of children (resp. number of roots)---and correspondingly the  size and complexity of the (indecomposable) algebraic system $I$ to be solved---could be arbitrarily large as a function of the size of the input system. This difficulty can persist even after optimal parametrization of the indecomposable system $I$ as in \cite{sitharam2010optimized} to minimize its algebraic complexity.

@@

\medskip\noindent
\header{(a) Small DR-plan.}
We obtain a  parameterized family of systems $I_{\lambda_F}$---one for each value $\lambda_F$ for the parameters $F$,  all of which have small DR-plans. Thus, given a value $v$ for $\lambda_F$, the system $I_v$ can potentially be solved or realized easily once the orientation type of the solution is known  (when the DR-plan size is small enough).

@@

% \begin{proof}
%     The Cartesian realization space of $(H,\left<\delta_{E'},
%     \lambda_F\right>)$ is computed easily with a DR-plan of size 2,
%     and is the union of $2^t$ solutions (modulo orientation preserving
%     isometries) each with a distinct orientation type, where $t$ is
%     the number of triangles in the 2-tree $H$; here $\delta_{S}$ is
%     the restriction of the length vector $\delta$ to the edges in $S$.
%     A desired solution $p$ (or connected component of a solution
%     space) of $(G,\delta)$ of an orientation type $\sigma_p$ can be
%     found by a subdivided binary search   of the cartesian realization
%     space of $(H, \left<\delta_{E'}, \lambda_F\right>)$ of orientation
%     type $\sigma_p$ - as $\lambda_F$ ranges over the discretized
%     convex polytope $\Phi_F(G',\delta_E')$ with bounding hyperplanes
%     described in Theorem \ref{theorem:convexcayley}. A solution $p$
%     is found  when the lengths for nonedges in $D$ match $\delta_D$.
% \end{proof}
%
% \begin{figure*}\centering
% \begin{subfigure}{.2\linewidth}\centering
%     \input{img/tikz/omd_k33_example_new-0.tikz}
%     \caption{}\label{fig:omd_k33_example:a}
% \end{subfigure}\hfill
% \begin{subfigure}{.15\linewidth}\centering
%     \input{img/tikz/omd_k33_example_new-1.tikz}
%     \caption{}\label{fig:omd_k33_example:b}
% \end{subfigure}
% \begin{subfigure}{.15\linewidth}\centering
%     \input{img/tikz/omd_k33_example_new-2.tikz}
%     \caption{}\label{fig:omd_k33_example:c}
% \end{subfigure}\hfill
% \begin{subfigure}{.15\linewidth}\centering
%     \input{img/tikz/omd_k33_example-1.tikz}
%     \caption{}\label{fig:omd_k33_example:d}
% \end{subfigure}
% \begin{subfigure}{.15\linewidth}\centering
%     \input{img/tikz/omd_k33_example-2.tikz}
%     \caption{}\label{fig:omd_k33_example:e}
% \end{subfigure}

% \caption{
% (\ref{fig:omd_k33_example:a}) The $K_{3,3}$ with two labeled edges, $e_1$ and $e_2$. (\ref{fig:omd_k33_example:b}) The $K_{3,3}$ with $e_1$ and $e_2$ removed (dashed lines) and rearranged to illustrate that it is now a partial 2-tree. (\ref{fig:omd_k33_example:c}) The $K_{3,3}$ with $\{e_1,e_2\}$ removed and $\{f_1,f_2\}$ (bold lines) added to make a 2-tree, showing that the $K_{3,3}$ is at least $OMD_2$. (\ref{fig:omd_k33_example:d}) The $K_{3,3}$ with only $e_2$ removed (dashed line). (\ref{fig:omd_k33_example:e}) The $K_{3,3}$ with $e_2$ removed and $f_3$ (bold line) added to make a low Cayley complexity graph, showing that the $K_{3,3}$ is $OMD_1$.
% }
% \label{fig:omd_k33_example}
% \end{figure*}

\ClearMyMinHeight
\SetMyMinHeight{.2}{img/epsfromtikz/omd_k33_example_new-0}
\SetMyMinHeight{.15}{img/epsfromtikz/omd_k33_example_new-1}
\SetMyMinHeight{.15}{img/epsfromtikz/omd_k33_example_new-2}
\SetMyMinHeight{.15}{img/epsfromtikz/omd_k33_example-1}
\SetMyMinHeight{.15}{img/epsfromtikz/omd_k33_example-2}

\begin{figure*}\centering
    \begin{subfigure}{.2\linewidth}\centering
        \includegraphics[height=\myMinHeight]{img/epsfromtikz/omd_k33_example_new-0}
        \caption{}\label{fig:omd_k33_example:a}
    \end{subfigure}\hfill
    \begin{subfigure}{.15\linewidth}\centering
        \includegraphics[height=\myMinHeight]{img/epsfromtikz/omd_k33_example_new-1}
        \caption{}\label{fig:omd_k33_example:b}
    \end{subfigure}
    \begin{subfigure}{.15\linewidth}\centering
        \includegraphics[height=\myMinHeight]{img/epsfromtikz/omd_k33_example_new-2}
        \caption{}\label{fig:omd_k33_example:c}
    \end{subfigure}\hfill
    \begin{subfigure}{.15\linewidth}\centering
        \includegraphics[height=\myMinHeight]{img/epsfromtikz/omd_k33_example-1}
        \caption{}\label{fig:omd_k33_example:d}
    \end{subfigure}
    \begin{subfigure}{.15\linewidth}\centering
        \includegraphics[height=\myMinHeight]{img/epsfromtikz/omd_k33_example-2}
        \caption{}\label{fig:omd_k33_example:e}
    \end{subfigure}

@@

% \noindent
% \note A major advantage of the convex Cayley method is that it is completely unaffected when $\delta$ are intervals rather than exact values~~\cite{sitharam2010convex}.

\sidenote{A major advantage of the convex Cayley method is that it is completely unaffected when $\delta$ are intervals rather than exact values~~\cite{sitharam2010convex}.}
%cite my paper with Heping!!!

\myexample
[Using Cayley configuration space].
A graph $G=K_{3,3}$  cannot be decomposed into any nontrivial isostatic graphs, i.e, its DR-plan has a root and 9 children corresponding to the 9 edges. Solving or recombining the system $(G,\delta)$ corresponding to the root of this DR-plan involves solving a quadratic system with 8 equations and variables. Instead of simultaneously solving this system, we could instead use the fact that $G=K_{3,3}$ is in OMD$_2$: remove the edges $e_1,e_2$ in Figure \ref{fig:omd_k33_example} to give a partial 2-tree $G'$. Now add the non-edges $f_1,f_2$ to give a 2-tree $H$ with a DR-plan of size 2. The Cayley configuration space $\Phi_f(G', \delta_{E\setminus e})$ is a single interval of attainable length values $\lambda_F$ for the edge $f$. When $\delta$ is generic, i.e, does not admit collinearities or coincidences in the realizations of $(G,\delta)$, the realization space of $(H, \left<\delta_{E\setminus e}, \lambda_f\right>)$ has 16 solutions $q^p_{\lambda_f}$ (modulo orientation preserving isometries), with distinct orientation types $\sigma_p$ (two orientation choices for each of the 4 triangles) that can be obtained by solving a sequence of 4 single quadratics in 1 variable (DR-plan of size 2). By subdivided binary search in the interval $\lambda_f \in \Phi_f(G', \delta_{E\setminus e})$, the desired solution $p$  of $(G,\delta)$ is found when the length of the nonedge $e$ in  the realization $q^p_{\lambda_f}$ is $\delta_e$.

In fact, we can show that $G=K_{3,3}$ is in OMD$_1$ by removing a single edge to reduce (as shown in Figure \ref{fig:omd_k33_example}) to a tree-decomposable graph of low Cayley complexity (which includes the class of partial 2-trees). In the next Section \ref{sec:tdecomp}, we discuss this issue of why the largest class of reduced graphs is desirable.
%
\subsection{Optimized Modification by Enlarging the class of Reduced
Graphs}
\label{sec:tdecomp}
%
It is possible in principle to decrease $k$ for a OMD$_k$ graph (i.e, the number of edges to be removed to ensure an isostatic completion that is decomposable with a small DR-plan) by considering reduced graphs $G'$ (and modified graphs $H$) that come from a larger class than partial 2-trees but nevertheless have convex Cayley configuration spaces at least when the realization space is restricted to a sufficiently comprehensive orientation type. In particular, the so-called \dfn{tree-decomposable graphs of low Cayley complexity} \cite{sitharam2011cayleyI,sitharam2011cayleyII} include the partial 2-trees and many others that are not partial 2-trees. See an illustration in Figure \ref{fig:omd_k33_example}. These too result in DR-plans of size 2 or 3, putting $G$ in the class OMD$_k$ and thus meeting Criteria (a) and (b). The Criterion (c) is met---for example when $k=1$---because 1-dof Cayley configuration spaces of linkages based on such graphs $G'$ are known to be single intervals when a comprehensive orientation type $\sigma_p$ of the sought solution $p$ is given. In addition, the bounds of these intervals are of low algebraic complexity. More precisely, the bounds  can themselves be computed using a DR-plan of size 2 or 3, i.e, the computation of these bounds is tree-decomposable. Alternatively, the bounds are in a simple quadratic or radically solvable extension field over the rationals, or can be computed by solving a triangularized system of quadratics.

### 2015-02-16 doc/GMP2015/revision_1/s05_problems.tex
Compiles with Elsevier format. Got rid of minor spacing errors. Converted tikz figures to eps. Aligned subfigures. Etc. It's looking good! Now to consider major changes.

\section{Problem Relationships and Unification}
\label{sec:table}
In this section we provide a unified view of  the various problems
studied in the previous 2 sections, along with formal reductions
between them, and relationships to other known problems and results as
well as open questions.
%
\subsection{Special classes of small DR-plans}
As seen in the previous section, 2-trees and tree-decomposable graphs
have not only small, but also special DR-plans that permit easy
solving --- essentially a single quadratic at a time.

@@

We discuss the complexity of the restricted
OMD problem (when $k$ is part of the input)
in Section \ref{sec:futurework}.

>>>>

\section{Problem Relationships and Unification}
\label{sec:table}
In this section we provide a unified view of  the various problems studied in the previous 2 sections, along with formal reductions between them, and relationships to other known problems and results as well as open questions.
%
\subsection{Special classes of small DR-plans}
As seen in the previous section, 2-trees and tree-decomposable graphs have not only small, but also special DR-plans that permit easy solving---essentially a single quadratic at a time.

@@

We discuss the complexity of the restricted OMD problem (when $k$ is part of the input) in \ref{sec:futurework}.

### 2015-02-16 doc/GMP2015/revision_1/s06_problempinning.tex
Compiles with Elsevier format. Got rid of minor spacing errors. Converted tikz figures to eps. Aligned subfigures. Etc. It's looking good! Now to consider major changes.

\begin{figure}\centering
    \includegraphics[width=0.4\linewidth]{img/Silica} \hspace{0.5cm}
    \raisebox{0.3\height}{\includegraphics[width=0.2\linewidth]{img/Silicon_tetrahedron}}
    \caption{Example of a single monolayer of a Silica (silicon and oxygen)
    glassy structure. This can be thought of as a triangle-multipin qusec
where the Silicon atoms are the triangles and the Oxygen atoms are the pins.
Not shown here are other monolayers stacked on this one. Each Silicon atom
has the structure seen to the right, and so binds to another Oxygen atom in
an adjacent monolayer. Pictures taken from \cite{silica_figure} and \cite{tetra_silica_figure}.}
    \label{fig:silica_glass}
\end{figure}

@@

\begin{remark}
\label{rem:bodypin_is_barjoint}
    A body-hyperpin qusecs is a special case of bar-joint qusecs of the
    first 5 sections. As such, the DR-planning for isostatics discussed in Section
    \ref{sec:DRP} is unchanged and the results of Section \ref{sec:recomb} will still go through with slight modifications.
\end{remark}

@@

\begin{definition}
\label{def:body-pin}
    A body-pin graph is a body-hyperpin graph with the following conditions:
    (1) each pin is shared by at most two bodies; and
    (2) no two bodies share more than one pin

@@

\begin{figure*}\centering
\begin{subfigure}{0.2\linewidth}\centering
    \includegraphics[width=\linewidth]{img/bodypin}
    \caption{}
\end{subfigure}
%
\begin{subfigure}{0.2\linewidth}\centering
    \input{img/tikz/bodypin_graph.tikz}
    \caption{}
\end{subfigure}
%
\begin{subfigure}{0.35\linewidth}\centering\scriptsize
    \input{img/tikz/bodypin_drp.tikz}
    \caption{}
\end{subfigure}
%
\begin{subfigure}{0.2\linewidth}\centering
    \includegraphics[width=\linewidth]{img/bodypin2}
    \caption{}
\end{subfigure}
%
\caption{(a) is a 1-dof body-pin graph. (b) is the corresponding body-bar graph explained in Definition \ref{def:body-pin}. (c) is the 1-dof DR-plan for the graph. In this case, to obtain an isostatic system, we would need to add a body and 2 pins to one of the nodes in the second level. (d) is the result of adding one such body to the bold-faced node.}
%
\end{figure*}
The above discussion leads to the main theorem:
\begin{theorem}
\label{thm:1dofcase}
    Given a 1-dof body-pin or triangle-multipin graph $G$ and corresponding
    1-dof DR-plan $T$, there is a quadratic algorithm for the 1-dof optimal
    completion problem of Section \ref{sec:recomb}.
\end{theorem}

@@

\begin{observation}
\label{obs:algebraic_completion}
    While the proof for Theorem \ref{thm:1dofcase} gives us a DR-plan for
    the isostatic completion with minimum fan-in, (a reasonable
    measure of algebraic complexity), a more nuanced
    measure that treats solutions of 1-dof and 2-dof systems as
    1- or 2- parameter families would no longer permit the algorithm given
    in the proof. In particular the complexity of the standard algorithm in the k-dof
    case would be exponential in $k$ (even if that case were matroidal and
    an optimal DR-plan is known).
\end{observation}

>>>>

\begin{figure}\centering
    \includegraphics[width=0.4\linewidth]{img/Silica}\hspace{0.5cm}
    \raisebox{0.3\height}{\includegraphics[width=0.2\linewidth]{img/Silicon_tetrahedron}}
    \caption{Example of a single monolayer of a Silica (silicon and oxygen) glassy structure. This can be thought of as a triangle-multipin qusec where the Silicon atoms are the triangles and the Oxygen atoms are the pins. Not shown here are other monolayers stacked on this one. Each Silicon atom has the structure seen to the right, and so binds to another Oxygen atom in an adjacent monolayer. Pictures taken from \cite{silica_figure} and \cite{tetra_silica_figure}.}
    \label{fig:silica_glass}
\end{figure}

@@

\begin{remark}\label{rem:bodypin_is_barjoint}
    A body-hyperpin qusecs is a special case of bar-joint qusecs of the
    first 5 sections. As such, the DR-planning for isostatics discussed in Section
    \ref{sec:DRP} is unchanged and the results of Section \ref{sec:recomb} will still go through with slight modifications.
\end{remark}

@@

\begin{definition}\label{def:body-pin}
    A body-pin graph is a body-hyperpin graph with the following conditions:
    (1) each pin is shared by at most two bodies; and
    (2) no two bodies share more than one pin

@@

\ClearMyMinHeight
\SetMyMinHeight{.2}{img/bodypin}
\SetMyMinHeight{.2}{img/epsfromtikz/bodypin_graph}
\SetMyMinHeight{.35}{img/epsfromtikz/bodypin_drp}
\SetMyMinHeight{.2}{img/bodypin2}

\begin{figure*}\centering
    \begin{subfigure}{0.2\linewidth}\centering
        \includegraphics[height=\myMinHeight]{img/bodypin}
        \caption{}\label{fig:bodypindrp:a}
    \end{subfigure}
    %
    \begin{subfigure}{0.2\linewidth}\centering
        \includegraphics[height=\myMinHeight]{img/epsfromtikz/bodypin_graph}
        \caption{}\label{fig:bodypindrp:b}
    \end{subfigure}
    %
    \begin{subfigure}{0.35\linewidth}\centering
        \includegraphics[height=\myMinHeight]{img/epsfromtikz/bodypin_drp}
        \caption{}\label{fig:bodypindrp:c}
    \end{subfigure}
    %
    \begin{subfigure}{0.2\linewidth}\centering
        \includegraphics[height=\myMinHeight]{img/bodypin2}
        \caption{}\label{fig:bodypindrp:d}
    \end{subfigure}
    %
    \caption{(\ref{fig:bodypindrp:a}) is a 1-dof body-pin graph. (\ref{fig:bodypindrp:b}) is the corresponding body-bar graph explained in Definition \ref{def:body-pin}. (\ref{fig:bodypindrp:c}) is the 1-dof DR-plan for the graph. In this case, to obtain an isostatic system, we would need to add a body and 2 pins to one of the nodes in the second level. (\ref{fig:bodypindrp:d}) is the result of adding one such body to the bold-faced node.}
    %
\end{figure*}

The above discussion leads to the main theorem:
\begin{theorem}
\label{thm:1dofcase}
    Given a 1-dof body-pin or triangle-multipin graph $G$ and corresponding 1-dof DR-plan $T$, there is a quadratic algorithm for the 1-dof optimal completion problem of Section \ref{sec:recomb}.
\end{theorem}

@@

\begin{observation}
\label{obs:algebraic_completion}
    While the proof for Theorem \ref{thm:1dofcase} gives us a DR-plan for the isostatic completion with minimum fan-in, (a reasonable measure of algebraic complexity), a more nuanced measure that treats solutions of 1-dof and 2-dof systems as 1- or 2- parameter families would no longer permit the algorithm given in the proof. In particular the complexity of the standard algorithm in the $k$-dof case would be exponential in $k$ (even if that case were matroidal and an optimal DR-plan is known).
\end{observation}
